Categorical Predictor Embeddings in Actuarial Modeling

### 2021-03-10 manuscript/manuscript.Rmd
edits

1. A GLM with gamma distribution and log link function,
2. A linear model with categorical embeddings and an exponential output activation,
3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2, and
4. A multilayer perceptron model with categorical embeddings.

@@

### Model 1: Simple GLM

@@

### Model 2: Linear Model with Embeddings

For the neural net, we utilize the same response variable, amount paid on building claim. We perform the following 
transformations on the predictor variables:

- Normalize the numeric variable ***building insurance coverage*** (center by mean and scale by standard deviation), 
- One-hot encode the **primary residence** variable, and 
- Apply embedding layers of dimension one to the rest of the categorical variables.

In terms of architecture, we connect the embeddings and the normalized numeric variable to a single output unit with 
softplus activation, where the softplus function is defined to be

@@

```{r nn-1, echo = FALSE, fig.cap = "blahblah", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/nn.png")
```

(maybe include a second nn with actual hidden layers?)

>>>>

1. A GLM with gamma distribution and log link function,
2. A neural network with unidimensional categorical embeddings,
3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2,
4. A neural network with multidimensional categorical embeddings.

@@

### Model 1: GLM

@@

### Model 2: Neural Network with Unidimensional Embeddings

For Model 2, we build a feedforward neural network. The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being sent to a single linear layer of 16 units. A ReLU activation
is then applied to the outputs before they are sent to a final linear layer resulting in a scalar. To constrain
predictions to be positive, we apply softplus activation, which is defined to be

@@

```{r nn-1, echo = FALSE, fig.cap = "blahblah", out.width = "90%", fig.align = "center"}
knitr::include_graphics("images/nn.png")
```

### Model 3: GLM with Neural Network Embeddings

### Model 4: Neural Network with Multidimensional Embeddings
